### 2014-07-19 writeups/code-deep-review.tex
Add code guide, B-damping code; check f(E,x) funcs
Added model code guide oriented towards how to use, fit with code.
Add Sean's B-damping version of code from email.
Reviewed and made small edits to electron distribution function
calculations in model code.  Finished reviewing Sean's model code.

@@

% ----------
% Appendix A
% ----------
\section*{Appendix A: clarifying code implementation of various equations}

@@

% Diffusion coeff
\subsection*{Scaled diffusion coefficient $\eta_2$}

@@

% Emissivity calculation / integration
\subsection*{Synchrotron emissivity integration (equation (20))}

@@

% Electron distribution integrals
\subsection*{Electron distribution calculations}

For $\mu < 1$, we have equation (15) implemented with... (for the general case)
Define $n = 1 - t^2$, as a change of variables ($dn$ to $dt$).
\[
    \text{argexp} = \frac{n^{1/(1-\mu)} E}{E_{\mt{cut}}}
    + \frac{(1 - \mu)
        \left[ l_{\mt{ad}}/\alpha \left(1 - n^{1/(1-\mu)}\right) - x \right]^2}
        {4 l_{\mt{diff}}^2 (1-n) / \alpha}
\]
with integrand:
\[
    2 (1 - t^2)^{ (s+\mu-2) / (1-\mu) } \exp(-\text{argexp})
\]
and normalization:
\[
    \frac{Q_0}
    {2 \sqrt{ \pi \alpha b B^2 \frac{\eta E_h^{1-\mu} C_d}{B} (1-\mu) }}
    E^{ -(\mu/2 + 1/2 + s)}
\]

% ----------
% Appendix B
% ----------
\section*{Appendix B: synchrotron power spectrum and parameters}

@@

\subsection*{Sanity checks on constants}

>>>>

\tableofcontents

@@

% ==========
% Appendix A
% ==========
\appendix
\section*{Appendices}
\section{Code implementation of various equations}

@@

% ---------------
% Diffusion coeff
% ---------------
\subsection{Scaled diffusion coefficient \texorpdfstring{$\eta_2$}{eta2}}

@@

% ------------------------------------
% Emissivity calculation / integration
% ------------------------------------
\subsection{Synchrotron emissivity integration (equation (20))}

@@

% -------------------------------
% Electron energy spectrum cutoff
% -------------------------------
\subsection{Electron energy spectrum cutoff}
I don't fully understand Sean's discussion of the effects of including a cutoff
or not -- nor the theoretical/experimental justification, for having a cutoff
in the spectrum (need to read papers...).  Nevertheless, I can stare at
equations and match symbols up.

Sean's original code (loss-limited only) writes:
\[
    E_{\mt{cut}} = \left[ 8.3 \left( \frac{B_0}{100 \unit{\mu G}} \right)^{-1/2}
                          \left( \frac{4 v_d}{10^8 \unit{cm\;s^{-1}}} \right)
                          1.6021773
                   \right]^{2/(1+\mu)}
                   \left( \frac{1}{\eta E_h^{(1-\mu)}} \right)^{1/(1+\mu)}
\]
The magnetic damping version of the code writes:
\[
    E_{\mt{cut}} = 8.3 \left( \frac{B_0}{100 \unit{\mu G}} \right)^{-1/2}
                   \left( \frac{4 v_d}{10^8 \unit{cm\;s^{-1}}} \right)
                   1.6021773
\]
The random factor of $1.6021773$ converts from TeV to ergs (since we are
working in Gaussian CGS units). Ahhhh

The other issue -- the exponent on the $B_0$ term should be $-1/(1+\mu)$, and I
don't know why the giant $2/(1+\mu)$ exponent is spanning several things.

Okay, time to try rederiving $E_{\mt{cut}}$.  Then, email Sean...

% -------------------------------
% Electron distribution integrals
% -------------------------------
\subsection{Electron distribution calculations}

First I'll reproduce the equations as seen in the code.  Then I'll 
simplify and make corrections as needed.  I have \emph{not} rederived the
equations from scratch.  In particular, I have no reference for the purely
advective solution (though it should be straightforward, if tedious, to
rederive).

% Pure advection (lad/ldiff > 30)
\subsubsection{Purely advective case}

If $l_{\mt{ad}} / l_{\mt{diff}} > 30$, Sean uses an analytic/easy solution to
the 1st order (linear, inhomogeneous) PDE:
\[
    v \frac{\ptl f}{\ptl x} - b B^2 E^2 \frac{\ptl f}{\ptl E}
    = 2 b B^2 E f + K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x)
\]
Sean's code gives the solution:
\[
    f(E,x) = (E_0(x))^{-s} \left(\frac{E_0(x)}{E}\right)^2
    \exp \left[ -E_0(x)/E_{\mt{cut}} \right] \cdot \left(8\times10^{-9}\right)
\]
where $E_0 = E / (1 - x/(v\tau_{\mt{synch}}))$.
If $x / (v \tau_{\mt{synch}}) > 1$, Sean sets $f(E,x) = 0$ (qualitatively makes
sense, but is this correct?).
The solution is repeated 3 times in Sean's code (for $\mu > 1$, $\mu < 1$, and
$\mu = 1$) but appears the same each time.  This is as expected, since $\mu$
does not matter if we neglect diffusion.

It is also worth noting that the ratio $l_{\mt{ad}} / l_{\mt{diff}}$ is a
rescaled Peclet number.  Write:
\[
    \frac{l_{\mt{ad}}}{l_{\mt{diff}}}
    = \frac{ v_d \tau_{\mt{synch}} }{ \sqrt{D \tau_{\mt{synch}}} }
    = \sqrt{ \frac{ v_d^2 \tau_{\mt{synch}} }{ D } }
    = \sqrt{ \frac{ v_d l_{\mt{ad}} }{ D } }
    = \sqrt{\mt{Pe}}
\]
and thus Sean neglects diffusion for $\mt{Pe} > 900$.

% General solution, remarks
\subsubsection{General solutions -- some general notes}

For all solutions, $z(x) = x$ as we assume constant magnetic field (i.e., no
magnetic damping model here).

The normalizations are NOT given in Sean's paper, but appear to follow
Lerche \& Schlickeiser (1980) and Rettig \& Pohl (2012).  The variable
$D_0 = \eta E_h^{1-\mu} C_d / B = D(E) / E^\mu$ is oft-seen in these
normalizing prefactors.  This is simply the scaling constant for $D(E)$, though
not really used in Sean's paper.

Additionally, the synchrotron cooling time constant $b = 1.57 \times 10^{-3}$
is defined as {\tt{a}} in Sean's code, to avoid conflict with magnetic field
$B$.

The distribution equations are near identical for $\mu > 1$ and $\mu < 1$,
but the limits are not the same.  Hence the distinct numerical implementations.

% mu < 1
\subsubsection{Solution for \texorpdfstring{$\mu < 1$}{mu lt 1}}
Change variables and evaluate equation (15) as a single integral.
Let $n = 1 - t^2$. Then $dn = -2t dt = -2\sqrt{1-n}dt$;
this kills the denominator $\sqrt{1-n}$.  Numerically integrate:
\[
    f(E,x) = \frac{Q_0 E^{-(\mu/2 + 1/2 + s)}}
            {2 \sqrt{\pi \alpha b B^2 D_0 (1-\mu)}} 
            \int_0^1 dt 2 (1-t^2)^{ (s+\mu-2) / (1-\mu) }
            \exp[ - \mathtt{argexp} ]
\]
with exponential argument
\[
    \mathtt{argexp} = \frac{n^{-1/(1-\mu)} E}{E_{\mt{cut}}}
    + \frac{(1 - \mu)
        \left[ l_{\mt{ad}}/\alpha \left(1 - n^{1/(1-\mu)}\right) - x \right]^2}
        {4 l_{\mt{diff}}^2 (1-n) / \alpha}
    \text{ .}
\]
If $n=1$ ($t=0$), Sean sets $\mathtt{argexp} = 10^{35}$ to prevent blowup.
This zeroes the integrand (recall we are performing a sum).

% mu = 1
\subsubsection{Solution for \texorpdfstring{$\mu = 1$}{mu eq 1}}
Break equation (14) into a two piece integral.
The first piece integrates over $n\in [1,e]$ ($t\in[0,1]$).
Let $n = e^{t^2}$ with $dn = 2 n \sqrt{\ln(n)} dt$.
This kills the denominator $\sqrt{\ln(n)}$.

The second piece integrates over $n=[e,\infty)$ ($y\in[0,1]$).
Change variables as:
\begin{align*}
    n &= \frac{y}{(1-y^2)^q} + n_{\mt{min}} \\
    dn &= \left( \frac{1}{(1-y^2)^q} + \frac{2qy^2}{(1 - y^2)^{q+1}} \right) dy
\end{align*}
where $n_{\mt{min}} = e$ and $q = 2$ appears to be an arbitrary exponent (?).

Now, the piece-wise integral is:
\[
    \frac{Q_0 E^{-(1+s)}}
         { 2 \sqrt{ \pi \alpha b B^2 D_0 } }
    \left[
        \int_0^1 dt \; 2 e^{(1-s) t^2} \exp[ - \mathtt{argexp} ]
        \; + \;
        \int_0^1 dy \left(\frac{(2q-1) y^2 + 1}{(1 - y^2)^{q+1}}\right)
                    \left(\frac{n^{-s}}{ \sqrt{\ln(n)} }\right)
                    \exp[ - \mathtt{argexp} ]
    \right]
\]
with exponential argument (same for both integrals):
\[
    \mathtt{argexp} = \frac{n E}{E_{\mt{cut}}}
        + \frac{ \left[ l_{\mt{ad}}/\alpha (1 - 1/n) - x \right]^2 }
        { 4 l_{\mt{diff}}^2 /alpha \ln(n) }
    \text{ .}
\]

% mu > 1
\subsubsection{Solution for \texorpdfstring{$\mu > 1$}{mu gt 1}}
Break equation (16) into a two piece integral.
The first piece integrates over $n\in[1,2]$ ($t\in[0,1]$).
Change variables as $n=1+t^2$ with $dn = 2\sqrt{n-1} dt$.
This kills the denominator $\sqrt{n-1}$.

The second piece integrates over $n\in[2,\infty]$ ($y\in[0,1]$).
Change variables as $n = y / (1-y^2)^q + n_{\mt{min}}$ again,
but with $n_{\mt{min}} = 2$ this time!

Now, the piece-wise integral is:
\begin{align*}
    \frac{Q_0 E^{-(\mu/2 + 1/2 + s)}}
         {2 \sqrt{\pi\alpha b B^2 D_0 (\mu-1)}}
    \biggl[
        &\int_0^1 dt \; 2 (1+t^2)^{(s+\mu-2)/(1-\mu)} \exp [ -\mathtt{argexp} ]
        \\
        & +\;
        \int_0^1 dy \left(\frac{(2q-1) y^2 + 1}{(1-y^2)^{q+1}}\right)
                    \left(\frac{n^{(s+\mu-2)/(1-\mu)}}{\sqrt{n-1}}\right)
                    \exp[ - \mathtt{argexp}]
    \biggr]
\end{align*}
with exponential argument (same for both integrals):
\[
    \mathtt{argexp} = \frac{n^{-1/(1-\mu)} E}{E_{\mt{cut}}}
    + \frac{(1 - \mu)
        \left[ l_{\mt{ad}}/\alpha \left(1 - n^{1/(1-\mu)}\right) - x \right]^2}
        {4 l_{\mt{diff}}^2 (1-n) / \alpha}
    \text{ .}
\]
This is the same $\mathtt{argexp}$ as for the $\mu < 1$ case.

% ----------
% Appendix B
% ----------
\section{Synchrotron power spectrum and parameters}

@@

\subsection{Synchrotron power spectrum derivation}

This follows Condon and Ransom's ERA, and Pacholczyk.

\subsection{Sanity checks on constants}
